SunPy - Python for Solar Physics

### 2014-01-28 3-2-HEK.tex
Second glob of edits

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import hek
>>> client = hek.HEKClient()
>>> tstart = '2011/08/09 00:00:00'
>>> tend = '2011/08/10 00:00:00'
# FL = flare
>>> event_type = 'FL'
>>> result = client.query(hek.attrs.Time(tstart,tend), 
...                       hek.attrs.EventType(event_type))
>>> len(result)
52
\end{minted}
\caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
which occurred on the 2011/08/09.}
\label{code:hek:simple}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import hek
>>> client = hek.HEKClient()
>>> tstart, tend = '2011/08/09 00:00:00', '2011/08/10 00:00:00'
>>> event_type = 'FL' # 'FL' indicates flare
>>> result = client.query(hek.attrs.Time(tstart,tend), 
...                       hek.attrs.EventType(event_type))
>>> len(result)
52
\end{minted}
\caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
which occurred on the 2011/08/09.}
\label{code:hek:simple}
\end{listing}

### 2014-01-28 3-3-HELIO.tex
Second glob of edits

#Obtain from all the catalogues these which name contain our event of interest
>>> catalogues = hc.get_table_names()
>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]

#Query all the catalogues that comes from cactus
>>> results = [hc.time_query(tstart, tend, event) 
...            for event in catalogues_event if 'cactus' in event]
>>> print results
********** This need to be added!
\end{minted}
\caption{Example of querying the HEC service.}
\label{code:helio}
\end{listing}

>>>>

# Obtain from all the catalogues these which name contain our event of interest
>>> catalogues = hc.get_table_names()
>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]

# Query all the catalogues that comes from cactus
>>> results = [hc.time_query(tstart, tend, event) 
...            for event in catalogues_event if 'cactus' in event]
>>> print results
********** This need to be added!
\end{minted}
\caption{Example of querying the HEC service.}
\label{code:helio}
\end{listing}
